An FMI-Based Initialization Plugin for INTO-CPS Maestro 2

### 2020-06-30 background.tex
case study equations (needs to be done by hand)

\subsection{FMU definitions}
To describe the formalization of FMUs, the vocabulary from Gomes et al\cite{gomes_lucio_vangheluwe_2019, Gomes2018} is adopted. The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information. This paper is only concerned with the initialization-phase of a co-simulation making time of an FMU irrelevant. The formalization from Gomes et al. is extended with new definitions regarding algebraic loops, and convergence of fixed point iteration.
\begin{definition}[FMU]\label{def:fmu}
  An FMU with identifier $c$ is represented by the tuple   
  $$\tuple{\stateset{c}, \inputs{c}, \outputs{c}, \fset{c}, \fget{c}},$$
  where:
  \begin{inparadesc}
    \item $\stateset{c}$ represents the state space;
    \item $\inputs{c}$ and $\outputs{c}$ the set of input and output variables, respectively;
    \item $\fset{c} : \stateset{c} \times \inputs{c} \times \values \to \stateset{c}$ and $\fget{c}: \stateset{c} \times \outputs{c} \to \values$ are functions to set the inputs and get the outputs, respectively (we abstract the set of values that each input/output variable can take as $\values$).
  \end{inparadesc}
\end{definition}

@@

As described by definition \ref{def:challenge} the algebraic loops introduce certain challenges in the system. This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}. It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step. The number of repetitions the operations should be be performed depends on the characteristics of the scenario. The operations should be performed until the system converge. 
An example of applying a fixed point iteration can be seen in Figure \ref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.

@@

However a fixed point iteration technique is not guaranteed to convergence if the system is unstable. This means that an upper bound of the number of repetitions needs to be established to ensure termination. In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario wouldn't be trustworthy. The criteria of a valid co-simulation scenario is is specified in definition \ref{def:convergence}.

>>>>

\subsection{FMU definitions}
To describe the formalization of FMUs, we adopt the vocabulary from \cite{gomes_lucio_vangheluwe_2019,Gomes2018}. The main definitions of relevance to this paper will be presented, but readers are referred to the original publications for more information. This paper is only concerned with the initialization-phase of a co-simulation making time of an FMU irrelevant. The formalization from Gomes et al. is extended with new definitions regarding algebraic loops, and convergence of fixed point iteration.
\begin{definition}[FMU]\label{def:fmu}
  An FMU with identifier $c$ is represented by the tuple   
  $$\tuple{\stateset{c}, \inputs{c}, \outputs{c}, \fset{c}, \fget{c}},$$
  where:
  \begin{inparadesc}
    \item $\stateset{c}$ represents the state space;
    \item $\inputs{c}$ and $\outputs{c}$ the set of input and output variables, respectively;
    \item $\fset{c} : \stateset{c} \times \inputs{c} \times \values \to \stateset{c}$ and $\fget{c}: \stateset{c} \times \outputs{c} \to \values$ are functions to set the inputs and get the outputs, respectively (we abstract the set of values that each input/output variable can take as $\values$).
  \end{inparadesc}
\end{definition}

@@

As described by definition \ref{def:challenge} the algebraic loops introduce certain challenges in the system. This means that algebraic loops needs to be handled using fixed point iterations\cite{Gomes2018}. It is a technique to repeatedly perform the steps of a sub-list of the co-simulation step \claudio{Co-simulation step? Aren't only considering initialization here?}. The number of repetitions the operations should be performed depends on the characteristics of the scenario. The operations should be performed until the values assigned to each variable no longer change. 
An example of applying a fixed point iteration can be seen in Figure \ref{def:fixedpoint} where a system containing an algebraic loop has to be initialized using fixed point iteration.
\claudio{Perhaps later you can ditch \cref{fig:fixedpont} and refer to the case study section, to shorten the text.}

@@

However a fixed point iteration technique is not guaranteed to convergence if the system is unstable. This means that an upper bound of the number of repetitions needs to be established to ensure termination. In case of a non-converging algebraic loop the simulation should be stopped since the result of the co-simulation scenario wouldn't be trustworthy. The criteria of a valid co-simulation scenario is specified in definition \ref{def:convergence}.

### 2020-06-30 initializationorder.tex
case study equations (needs to be done by hand)

In the \textit{Initialization Mode} state all variables of all FMUs should be defined.
The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order. This phase should should also support algebraic loops, this support includes utilization of fixed point iteration and detection of non-convergence of algebraic loops.

@@

As described earlier, not all co-simulation scenarios are valid, and these invalid scenarios need to be identified. This is done by monitoring convergence of all algebraic loops. A valid co-simulation scenario must convergence by definition given in definition \ref{def:convergence}.

>>>>

In the \textit{Initialization Mode} state all variables of all FMUs should be defined.
The variables with \textit{causality = parameter} of each FMU are set first, and the order of which they are set is again insignificant as they are independent.
Afterwards the interconnected variables should be defined, but as stated by the definitions \ref{def:feedthrough}, \ref{def:getout} and \ref{def:setin} the operations \textit{get} and \textit{set} \textbf{require} a specific initialization order, and algebraic loops places even more constraints on the initialization order. This phase should also support algebraic loops, this support includes utilization of fixed point iteration and detection of non-convergence of algebraic loops.

@@

As described earlier, not all co-simulation scenarios are valid, and these invalid scenarios need to be identified. This is done by monitoring convergence of the fixed point iteration when solving the algebraic loops. A valid co-simulation scenario must convergence by definition \ref{def:convergence}.
